Run models

### 2017-02-05 Code/run-models.Rmd
set 6 results

```{r fit_models}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame
system.time(
  for(sex_i in c("Male", "Female")){
    print(sex_i)
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    #for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
    #for(state_i in c("Florida", "Georgia", "Illinois", "Indiana")) { #saved as results_set_3  
    for(state_i in c("Iowa", "Kansas", "Kentucky", "Louisiana")) { #saved as results_set_4  
      print(state_i)
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

# r.White <- rbind(r.White.AlabamaMale, r.White.ArizonaMale, r.White.ArkansasMale, r.White.CaliforniaMale,
#                  r.White.AlabamaFemale, r.White.ArizonaFemale, r.White.ArkansasFemale, r.White.CaliforniaFemale)
# r.White <- rbind(r.White.Colorado.Male, r.White.Connecticut.Male, r.White.Delaware.Male, r.White.WashingtonDC.Male,
#                  r.White.Colorado.Female, r.White.Connecticut.Female, r.White.Delaware.Female, r.White.WashingtonDC.Female)
# r.White <- rbind(r.White.Florida.Male, r.White.Georgia.Male, r.White.Illinois.Male, r.White.Indiana.Male,
#                  r.White.Florida.Female, r.White.Georgia.Female, r.White.Illinois.Female, r.White.Indiana.Female)
r.White <- rbind(r.White.Iowa.Male, r.White.Kansas.Male, r.White.Kentucky.Male, r.White.Louisiana.Male,
                 r.White.Iowa.Female, r.White.Kansas.Female, r.White.Kentucky.Female, r.White.Louisiana.Female)
r.White$race <- "White"

# r.Black <- rbind(r.Black.AlabamaMale, r.Black.ArizonaMale, r.Black.ArkansasMale, r.Black.CaliforniaMale,
#                  r.Black.AlabamaFemale, r.Black.ArizonaFemale, r.Black.ArkansasFemale, r.Black.CaliforniaFemale)
r.Black <- rbind(r.Black.Iowa.Male, r.Black.Kansas.Male, r.Black.Kentucky.Male, r.Black.Louisiana.Male,
                 r.Black.Iowa.Female, r.Black.Kansas.Female, r.Black.Kentucky.Female, r.Black.Louisiana.Female)
r.Black$race <- "Black"
```

@@

#SET 4: Iowa, Kansas, Kentucky, Louisiana
save(r.All, le.calculations, file = "~/BW_results/results_set_4.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_4.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_4.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_4.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_4.csv")

>>>>

```{r fit_models}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame
system.time(
  for(sex_i in c("Male", "Female")){
    print(sex_i)
    #for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) { #saved as results_set_1
    #for(state_i in c("Colorado", "Connecticut", "Delaware", "Washington DC")) { #saved as results_set_2
    #for(state_i in c("Florida", "Georgia", "Illinois", "Indiana")) { #saved as results_set_3  
    #for(state_i in c("Iowa", "Kansas", "Kentucky", "Louisiana")) { #saved as results_set_4  
    # for(state_i in c("Maryland", "New York", "North Carolina", "Texas", "Virginia", "Wisconsin" )) { #saved as results_set_5  
    for(state_i in c("Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Nebraska" )) { #saved as results_set_6  
      print(state_i)
      assign(paste0("r.White.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", gsub(" ", "", state_i), ".", sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))
    }
  }
)

# r.White <- rbind(r.White.AlabamaMale, r.White.ArizonaMale, r.White.ArkansasMale, r.White.CaliforniaMale,
#                  r.White.AlabamaFemale, r.White.ArizonaFemale, r.White.ArkansasFemale, r.White.CaliforniaFemale)
# r.White <- rbind(r.White.Colorado.Male, r.White.Connecticut.Male, r.White.Delaware.Male, r.White.WashingtonDC.Male,
#                  r.White.Colorado.Female, r.White.Connecticut.Female, r.White.Delaware.Female, r.White.WashingtonDC.Female)
# r.White <- rbind(r.White.Florida.Male, r.White.Georgia.Male, r.White.Illinois.Male, r.White.Indiana.Male,
#                  r.White.Florida.Female, r.White.Georgia.Female, r.White.Illinois.Female, r.White.Indiana.Female)
# r.White <- rbind(r.White.Iowa.Male, r.White.Kansas.Male, r.White.Kentucky.Male, r.White.Louisiana.Male,
#                  r.White.Iowa.Female, r.White.Kansas.Female, r.White.Kentucky.Female, r.White.Louisiana.Female)
# r.White <- rbind(r.White.Maryland.Male, r.White.NewYork.Male, r.White.NorthCarolina.Male, r.White.Texas.Male, 
#                  r.White.Virginia.Male, r.White.Wisconsin.Male, 
#                  r.White.Maryland.Female, r.White.NewYork.Female, r.White.NorthCarolina.Female, r.White.Texas.Female, 
#                  r.White.Virginia.Female, r.White.Wisconsin.Female)
r.White <- rbind(r.White.Massachusetts.Male, r.White.Michigan.Male, r.White.Minnesota.Male, r.White.Mississippi.Male, 
                 r.White.Missouri.Male, r.White.Nebraska.Male, 
                 r.White.Massachusetts.Female, r.White.Michigan.Female, r.White.Minnesota.Female, r.White.Mississippi.Female, 
                 r.White.Missouri.Female, r.White.Nebraska.Female)
r.White$race <- "White"

# r.Black <- rbind(r.Black.AlabamaMale, r.Black.ArizonaMale, r.Black.ArkansasMale, r.Black.CaliforniaMale,
#                  r.Black.AlabamaFemale, r.Black.ArizonaFemale, r.Black.ArkansasFemale, r.Black.CaliforniaFemale)
r.Black <- rbind(r.Black.Massachusetts.Male, r.Black.Michigan.Male, r.Black.Minnesota.Male, r.Black.Mississippi.Male, 
                 r.Black.Missouri.Male, r.Black.Nebraska.Male, 
                 r.Black.Massachusetts.Female, r.Black.Michigan.Female, r.Black.Minnesota.Female, r.Black.Mississippi.Female, 
                 r.Black.Missouri.Female, r.Black.Nebraska.Female)
r.Black$race <- "Black"
```

@@

#SET 4: Iowa, Kansas, Kentucky, Louisiana
# save(r.All, le.calculations, file = "~/BW_results/results_set_4.Rdata") 
# write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_4.csv")
# write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_4.csv")
# write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_4.csv")
# write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_4.csv")

#SET 5: Maryland, New York, North Carolina, Texas, Virginia, Wisconsin
# save(r.All, le.calculations, file = "~/BW_results/results_set_5.Rdata") 
# write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_5.csv")
# write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_5.csv")
# write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_5.csv")
# write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_5.csv")

#SET 6: "Massachusetts", "Michigan", "Minnesota", "Mississippi", "Missouri", "Nebraska"
save(r.All, le.calculations, file = "~/BW_results/results_set_6.Rdata") 
write.csv(x = BlackWhite, file = "~/BlackWhiteMortalityGap/Results/BlackWhite_set_6.csv")
write.csv(x = age.decomp.estimates, file = "~/BlackWhiteMortalityGap/Results/age_decomp_set_6.csv")
write.csv(x = cod.marginal.estimates, file = "~/BlackWhiteMortalityGap/Results/cod_marginal_set_6.csv")
write.csv(x = age.cod.estimates, file = "~/BlackWhiteMortalityGap/Results/age_cod_set_6.csv")
```
